Efficient pedigree recording for fast population genetics simulation

### 2018-01-12 forwards_paper.tex
Added SDSL reference for succinct data structures.

In this paper, we describe a storage method for \emph{succinct tree sequences}
and, hence, genome sequence, as well as an algorithm for simplifying these.
The data structure is \emph{succinct} in the sense that its' space usage is close to optimal,
while still allowing efficient retrieval of information.
Both are implemented as improvements to the algorithmic tools and data structures in \msprime{}.
We also describe how these tools can efficiently record,
and later process, the embellished population pedigree from a forwards-time simulation.
While providing substantial savings in computational time and space, our methods provide much
more information than simply simulating the genomes -- the tree sequence
encodes all marginal genealogies of individuals living at the end of the simulation.
Although we were motivated by a need for more efficient genomic simulations,
these tools may prove more widely useful.

>>>>

In this paper, we describe a storage method for \emph{succinct tree sequences}
and, hence, genome sequence, as well as an algorithm for simplifying these.
The data structure is \emph{succinct} in the sense that its' space usage is close to optimal,
while still allowing efficient retrieval of information (see, e.g.,
\citet{gog2014theory}).
Both are implemented as improvements to the algorithmic tools and data structures in \msprime{}.
We also describe how these tools can efficiently record,
and later process, the embellished population pedigree from a forwards-time simulation.
While providing substantial savings in computational time and space, our methods provide much
more information than simply simulating the genomes -- the tree sequence
encodes all marginal genealogies of individuals living at the end of the simulation.
Although we were motivated by a need for more efficient genomic simulations,
these tools may prove more widely useful.
